Merging Datasets Through Deep learning

### 2018-08-31 paper2018/siamese_networks.tex
loss function edits

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{tanh_triplet}
        \caption{$Tanh$ loss}
        \label{tanh_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure*}

@@

\subsection{Hyperbolic Tangent Loss}

The inspiration for our loss is that triplet loss, in effect, only
pushes the negative distance as far as $\alpha$; if the negative
distance is larger than that, the total loss can become negative,
which is then forced to 0.  However, the further the negative point is
from the anchor, the better, so we want to push it as far away as
possible, without a limit like $\alpha$.  This is illustrated in
Figure~\ref{tanh_loss} by pushing toward $\infty$.  To achieve this,
we use hyperbolic tangent to compress all distances to the range 0 to
1, and substract the negative distance from 1.  Then our loss function
simply needs to minimize both positive and negative numbers:

\begin{equation}
  l_{triple} =  tanh\left(\|\bf{x_a} - \bf{x_p}\|\right) + \left(1-tanh\left(\|\bf{x_a} -\bf{x_n}\|\right)\right)
\label{tanh}
\end{equation}

>>>>

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure*}

@@

\subsection{Adapted Loss}

The inspiration for our loss is to separate the effect of the positive
and negative distances as much as possible.  Rather than subtracting
the negative distance from the positive one, we want to negate the
negtive distance and then add the two.  To approximate this, we
subtract the negative distance from a margin, and use 0 instead if
that difference is negative.  We then combine the squared distances as
usual, as how in Figure~\ref{adapted}.

\begin{equation}
  l_{triple} =  \|\bf{x_a} - \bf{x_p}\|^2 + \left[ \alpha - \|\bf{x_a} -\bf{x_n} \right]_+^2
\label{adapted}
\end{equation}
